Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-30 tex/Drafts/Draft-2.tex
Section 2 revisions.

  In the following section, we cite a theorem of James-Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row Specht modules.
  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is complicated and depends on the characteristic of $k$.
  We will focus primarily on the former case.

  Following this, we cite the branching theorems of Kleshchev-Brundan, which allow us to fully characterize the Socle of $\Res S^{\lambda}$.
  This and some combinatorial arguments allow us to come to the main result of this section, which may loosely be stated as follows:
  the composition series of $D^{(n+r,n)}$ is restrictive enough in many cases with $S^{(n+r,n)}$ irreducible and $e > n$ case that such a composition series uniquely characterizes irreducibles.
  This will be immensely useful later for characterizing $M$ via Specht modules, as it will include all cases with $e > n + r + 1$.

  \subsection{Irreducibility of $S^\lambda$}
  Let $k$ have characteristic $\ell$;
  then, set
  \[
    p := \begin{cases}
      \ell & \ell > 0\\
      \infty & \ell = 0
    \end{cases}.
  \]
  Note that $p = e$ when $q = 1$.
  For $h$ a natural number, let $\nu_p(h)$ be the $p$-adic evaluation of $h$.
  As a convention, set $\nu_\infty(h) = 0$ for all $h$.
  Define the function $\nu_{e,p} : \NN \rightarrow \cbr{-1} \cup \NN$ by
  \[
    \nu_{e,p}(h) := \begin{cases}
      \nu_p(h) & e \mid h\\
      -1 & e \nmid h
    \end{cases}.
  \]
  Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$.
  With this language, we may express the following theorem, part (ii) of which is named the \emph{carter criterion}, due to James-Mathas.\cite{Mathas-book}
  \begin{theorem}[James-Mathas]
    The following are equivalent:
    \begin{enumerate}[label={(\roman*)}]
      \item $S^{\lambda} \simeq D^{\lambda}$.
      \item $\lambda$ is $e$-regular and $S^\lambda$ is irreducible.
      \item $\nu_{e,p}\prn{h_{ab}^\lambda} = \nu_{e,p}\prn{h_{ac}^\lambda}$ for all nodes $(a,b)$ and $(a,c)$ in $\brk \lambda$.
    \qed\end{enumerate}
  \end{theorem}
  This result gives information solely on $e$-regular partitions, and the general irreducibility of $S^\lambda$ away from $p=2$ is not well understood.
  We will henceforth specialize slightly to the case that $(n+r,n)$ is $e$-restricted.

  \begin{corollary}\label{S irreducibility}
    If $r = 0$, assume $e > 2$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $e > n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
      \item Suppose $e \leq n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values.
    \end{enumerate}  
  \end{corollary}
  In the case that $\lambda = (n+r,n)$ and $e \nmid r+2,r+3,\dots,n+r+1$, say that $\lambda$ is \emph{$e$-top-indivisible}.
  Since no multiples of $e$ are in an interval of length $n$ in $\NN$, we have $e > n$, so this is precisely case (i) above.
  \begin{proof}
    The beginning condition implies that $\lambda$ is $e$-regular, which we will use below.

    \textbf{(i)}
    Note that $\nu_p(l) \neq -1$ for all $l$ and only hook lengths in the top row may vanish mod $e$;
    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the second column.
    These hook lengths are precisely $r + 2,\dots,n+r+1$.

    \textbf{(ii)}
    Note that we have $\nu_{e,p}\prn{h^\lambda_{n-e+1,2}} \neq -1$.
    Suppose that $e \nmid r + 1$.
    Then, \[\nu_{e,p}\prn{h^\lambda_{n-e+1,1}} = \nu_{e,p}\prn{h^\lambda_{n-e,2} + r + 1} = -1,\]
    giving $S^{(n+r,n)}$ reducible.

    \def\corsecsep{5pt}
    \vspace{\corsecsep}
    Now, suppose that $\nu$ acquires at least three values, and \[0 \leq \nu_{e,p}(h^{\lambda}_{ab}) < \nu_{e,p}\prn{h^{\lambda}_{a'b'}}\] and $S^{(n+r,n)}$ is irreducible.
    If $b=b'$ then we have reducibility, so assume $b \neq b'$.
    Further, if $a = a'$, then we may replace $a$ with the other column;
    hence we may assume WLOG that $a \neq a'$ as well.

    Note that $p$-adic valuation is monotonic, so $h^\lambda_{ab} < h^\lambda_{a'b'}$.
    If $(a,b)$ is in the rightmost $r$ columns, then we may $0 \leq \nu_{e,p}\prn{h^\lambda_{a''b''}} \leq \nu_{e,p}\prn{h^\lambda_{ab}}$ for some $(a'',b'')$ in the rightmost $n$ columns;
    this has the same hook length as a cell in the leftmost $n$ columns and bottom row, so we may assume $(a,b)$ is not in the rightmost $r$ columns.
    Similar logic allows us to assume $(a',b')$ is in the leftmost $n$ columns as well.

    If $b < b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'}) < \nu(h_{a'b'})$ while $h_{ab'} > h_{a'b'}$, a contradiction.
    If $b > b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'})$ and $h_{ab} < h_{ab'}$, so there is some $c < b$ with $\nu_{e,b}(h_{ab}) = \nu_{e,p}(h_{ac})$; we may replace $b$ with $c$, and repeat until $b = b'$ to reach contradiction.

    \vspace{\corsecsep}
    Finally, assume $e | r + 1$ and $\nu_{e,p}$ acquires two values.
    Since $e | r + 1$, $e \mid h_{a1}^\lambda$ iff $e \mid h_{a2}$;
    since $\nu_{e,p}$ acquires only two values, this proves that $\nu_{e,p}(h_{a1}) = \nu_{e,p}(h_{a2})$ across these rows, giving the lemma.
  \end{proof}

  From condition (ii) we see that irreducibiliy at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
  We will finish our discussion of irreducibilty of $S^\lambda$ via the following special cases of (ii) above.
  \begin{corollary}
    If $r = 0$, assume $e > 2$.
    Suppose $e \leq n$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $p > n + r + 1$. Then, $S^{(n + r,n)}$ is irreducible iff $e | r + 1$.
      \item Suppose $p = 2$. Then, $S^{(n+r,n)}$ is not irreducible.
    \end{enumerate}
  \end{corollary}
  \begin{proof}
    (i) is clear.
    (ii) is given by noting that $e + r + 1 \geq 2e$;
    then, $h_{n-e+1,1} - h_{n-e+1,2} \geq 1$, giving reducibility.
  \end{proof}
  \subsection{Branching}
  In this section as well as later sections, we will consider the restruction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions give isomorphic restrictions of representations (through a particular isomorphism of the subalgebras).
  We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.

  Throughout the rest of the paper, it will be useful to have precise notation;
  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as is standard, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.\cite{Kleshchev}

  Fixing some partition $\lambda \vdash 2n + r$, for $1 \leq i \leq j \leq l$, let $\beta_\lambda(i,j)$ and $\gamma_\lambda$ be the quantities
  \begin{align*}
    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t\\
    \gamma_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i+1}^j a_t.
  \end{align*}
  Results due to Kleshchev and Brundan refer to \emph{normal} and \emph{good} numbers;
  for these, we will use the facts that 1 is always normal and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
  Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}

  The following statements, collectively called \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev}\cite{Brundan} 
  They entirely characterize the Socle of $\Res D^\lambda$, as well as the condition that $\soc\prn{\Res D^\lambda} \simeq \Res D^\lambda$.
  \begin{theorem}[Kleshchev-Brundan]
    We have the following isomorphisms of vector spaces
    \begin{align*}
      \Homarg{\SH'}{S^\mu,\Res D^\lambda} 
      &\simeq \begin{cases}
        k & \mu \xrightarrow{\text{normal}} \lambda\\
        0 & \text{otherwise}
      \end{cases}\\
      \Homarg{\SH'}{D^\mu,\Res D^\lambda} 
      &\simeq \begin{cases}
        k & \mu \xrightarrow{\text{good}} \lambda\\
        0 & \text{otherwise}
      \end{cases}
    \end{align*}
    and $\Res D^\lambda$ is semisimple if and only if every normal number in $\lambda$ is good.\qed
  \end{theorem}

  Using this, we immediately see that, for any rectangular partition $(m^\ell)$, we have
  \[
    \Res D^{(m^\ell)} \simeq D^{(m^{\ell-1},m-1)}.
  \]
  The non-rectangular two-row case is more complicated, but we may still describe it fully as follows.
  \begin{corollary}\label{D Restrictions}
    Suppose $r > 0$.
    Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
    \[
      \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
        D^{(n + r - 1,n)} & e \mid r+2\\
        D^{(n + r,n-1)} & e \nmid r+2, \; e \mid r\\
        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
      \end{cases}.
    \]
    Further, when $e \nmid r$ or $e \mid r + 2$, $\Res D^{(n+r,n)}$ is semisimple.
  \end{corollary}
  \begin{proof}
    This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
    \begin{align*}
      \beta_\lambda(1,2) &= r + 2\\
      \gamma_\lambda(1,2) &= r
    \end{align*}
    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ iff $e \nmid r + 2$.
    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ iff 1 is good iff $e \nmid r$
  \end{proof}

  Now that we've characterized how these restrict, we can describe how strongly these restrictions characterize irreducibles.
  Namely, we will prove that a composition series consistent with $(n+r,n)$ and $e$ top-indivisibility of $(n+r-1,n+1)$ is sufficient to determine that an irreducible is $D^{(n+r,n)}$ when either $r \neq 0$ or $e \neq 4$.
  \begin{proposition}\label{Combinatorics}
    Let $\lambda$ be an $e$-regular partition of $2n + r$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r$.
        If $D^\lambda$ has the composition series 
        \begin{equation}\label{D Composition Series}
          0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
        \end{equation}
        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
        Then $\lambda = (n,n)$. 
    \end{enumerate}
  \end{proposition}
  \begin{proof}
    Note that $e > n$.

    \textbf{(i)}
    Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)$, and let $\mu := (n + r,n)$.
    Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda = \varpi,\varsigma,\mu$.
    We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series};
    then, we will have $\lambda = \mu$.

    Suppose that $\lambda = \varpi$.
    We will break into cases with $r$.
    \begin{itemize}
      \item Suppose that $r > 1$.
        Note that $e \nmid r + 1 = \beta_\varpi(1,2)$, so $2$ is normal.
        Further, $\gamma_\varpi(2,3) = n \not\equiv 0 \pmod e$, so 2 is good and $D^{(n+r-1,n-1,1)} \subset D^\varpi$, which is not a composition factor in \eqref{D Composition Series}.
        Hence, by Jordan-H\"older, $\lambda \neq \varpi$.\cite{Etingof}

      \item Suppose that $r = 1$.
        Then, $\varpi = (n,n,1)$ has $\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e$, giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$.
    \end{itemize} 
  \iffalse % keeping just in case
   \begin{align*}
    \beta_{\varpi}(1,2)     &= r + 1 \\
    \beta_{\varpi}(1,3)     &= n + r + 1 \\
    \beta_{\varpi}(2,3)     &= n + 1\\
    \gamma_{\varpi}(1,2)    &= r\\
    \gamma_{\varpi}(1,3)    &= n + r\\
    \gamma_{\varpi}(2,3)    &= n\\
  \end{align*}
  \fi

  \vspace{5pt}
  Now suppose that $\lambda = \varsigma$ and break into cases with $r$:
  \begin{itemize}
    \item Suppose $r > 2$.
      Then, by Corollary \ref{D Restrictions}, we require that $e \nmid r$ and $e \mid r - 2$;
      these are not satisfied, so $\lambda \neq \varsigma$.
    \item Suppose $r = 2$.
      Then $\Res \, D^\varsigma \simeq D^{(n+1,n)}$ is irreducible, contradicting \eqref{D Composition Series}. 
    \item Suppose $r < 2$. 
      Then $\varsigma$ is not a partition.
  \end{itemize}

  \textbf{(ii)}
  This result is easier than the previous result;
  since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
  This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
  if $\lambda = \varsigma$, then we have that $e \mid \beta_\varsigma(1,2) = 4$, a contradiction.
  Hence $\lambda = \mu$.
\end{proof}

@@

  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
  Then,
  \begin{align*}
    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
    &= 1 + \dots + q^{n + r}\\
    &= \brk{n + r + 1}_q.
  \end{align*}
  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
\end{proof}
\begin{theorem}\label{Irreducibility Theorem}
  Suppose that $(n+r,n)$ is $e$ top-indivisible.
  Then, the representation $M_{2n + r}^r$ is irreducible. 
\end{theorem}
\begin{proof}
  We proceed by induction on $n$.
  Note that, by identification with the trivial and sign representation, the base case $n = 0$ is already proven.

@@

\bibliographystyle{plain} 
 \bibliography{../RepBib}
\end{document}

>>>>

  Throughout the rest of the paper, it will be useful to have precise notation;
  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as in \cite{Kleshchev}, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
  Say that $\lambda$ is \emph{$e$-regular} if $\lambda_i - \lambda_{i+1} < e$ for all $i$ and $\lambda_l < e$.

  In the following subsection, we cite a theorem of James--Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row Specht modules.
  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is more complicated and depends also on the characteristic of $k$.
  We will focus primarily on the former case.

  Following this, we reproduce the branching theorems of Kleshchev--Brundan, which allow us to fully characterize the socle of $\Res D^{\lambda}$.
  This and some combinatorial arguments yield the main result of this section, which allows us to determine certain $D^{(n+r,n)}$ via their composition series.
  This will be instrumental later for characterizing the crossingless matchings representation $M_{2n + r}^r$ as a Specht module, and it will extend to all cases with $e > n + r + 1$.

  \subsection{Irreducibility of $S^\lambda$}
  Let $\ell$ be the characteristic of $k$;
  then, set
  \[
    p := \begin{cases}
      \ell & \text{if }\ell > 0,\\
      \infty & \text{if }\ell = 0.
    \end{cases}
  \]
  Note that $p = e$ when $q = 1$.
  For $h$ a natural number, let $\nu_p(h)$ be the $p$-adic valuation of $h$.
  By convention, set $\nu_\infty(h) = 0$ for all $h$.
  Define the function $\nu_{e,p} : \NN \rightarrow \cbr{-1} \cup \NN$ by
  \[
    \nu_{e,p}(h) := \begin{cases}
      \nu_p(h) & e \text{if }\mid h\\
      -1 & e \text{if }\nmid h
    \end{cases}.
  \]
  Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$ as defined in \cite{Kleshchev}.
  With this language, we may express the following theorem, parts (ii)-(iii) of which are known as the \emph{Carter criterion} in the symmetric group case, due to James--Mathas.\cite{Mathas-book}
  \begin{theorem}[James--Mathas]\label{Mathas Irreducibility}
    The following are equivalent:
    \begin{enumerate}[label={(\roman*)}]
      \item $S^{\lambda} \simeq D^{\lambda}$.
      \item $\lambda$ is $e$-regular and $S^\lambda$ is irreducible.
      \item $\nu_{e,p}\prn{h_{ab}^\lambda} = \nu_{e,p}\prn{h_{ac}^\lambda}$ for all nodes $(a,b)$ and $(a,c)$ in $\brk \lambda$.
    \qed\end{enumerate}
  \end{theorem}
  \begin{proof}
    See \cite{Mathas-book} theorem 5.42.
  \end{proof}
  This result gives information solely on $e$-regular partitions, and the general irreducibility of $S^\lambda$ away from $p=2$ is not well understood.
  We will henceforth specialize slightly to the case that $(n+r,n)$ is $e$-regular.

  \begin{corollary}\label{S irreducibility}
    If $r = 0$, assume $e > 2$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $e > n$.
        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid r + 2,r+3,\dots,n + r + 1$.
      \item Suppose $e \leq n$.
        If $S^{(n+r,n)}$ is irreducible, then $e \mid r + 1$.
    \end{enumerate}  
  \end{corollary}
  Note that the condition $e \nmid r+2,r+3,\dots,n+r+1$ implies that $e > n$.
  \begin{proof}
    Our initial assumption on $e$ implies that $\lambda$ is $e$-regular, which we will use below.

    \textbf{(i)}
    Note that $\nu_p(h) \neq -1$ for all naturals $h$ and only hook lengths in the top row may vanish mod $e$ by Figure \ref{Hooks};
    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the second row by Theorem \ref{Mathas Irreducibility}.
    These hook lengths are precisely $r + 2,\dots,n+r+1$.

    \textbf{(ii)}
    Note that we have $\nu_{e,p}\prn{h^\lambda_{2,n-e+1}} \neq -1$, and $\nu_{e,p}\prn{h^\lambda_{2,n+r}} = -1$ so $\nu_{e,p}$ acquires at least two values.
    Suppose that $e \nmid r + 1$.
    Then, \[\nu_{e,p}\prn{h^\lambda_{1,n-e+1}} = \nu_{e,p}\prn{h^\lambda_{2,n-e+1} + r + 1} = -1,\]
    giving $S^{(n+r,n)}$ reducible by Theorem \ref{Mathas Irreducibility}.
  \end{proof}

  \begin{figure}
  \ytableausetup{mathmode,boxsize=4.5em}
  \begin{ytableau}
    n+r+1 & n + r & \dots & r + 2 & r & r-1 & \dots & 1\\ 
    n & n-1 & \dots & 1
  \end{ytableau}
  \ytableausetup{mathmode,boxsize=normal}
  \caption{The young diagram corresponding to the partition $(n+r,n)$ with filled-in ook lengths.}\label{Hooks}
\end{figure}

  From part (i) we see that irreducibility at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
  We will finish our discussion of irreducibility of $S^\lambda$ via sharp characterization of the $e \leq n$ case.
  \begin{corollary}
    If $r = 0$, assume $e > 2$.
    Suppose $e \leq n$, and suppose $p > n + r + 1$.
    Then, $S^{(n+r,n)}$ is irreducible if and only if $e \mid r+1$.
  \end{corollary}
  \begin{proof}
    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturalls $h,h'$. 
  \end{proof}
  \subsection{Branching}
  In this section as well as later sections, we will consider the restriction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions are canonically isomorphic, and the corresponding restrictions are canonically isomorphic via this isomorphism of algebras.
  We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.

  Fixing some partition $\lambda \vdash 2n + r$, for $1 \leq i \leq j \leq l$, let $\beta_\lambda(i,j)$ and $\gamma_\lambda$ be the quantities
  \begin{align*}
    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t\\
    \gamma_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i+1}^j a_t.
  \end{align*}
  Note that $\beta_\lambda(i,j)$ is the hook length of cell $(a_1 + \dots + a_{i-1}+1,\lambda_j)$.

  Results due to Kleshchev and Brundan refer to \emph{normal} and \emph{good} numbers;
  for these, we will use the facts that 1 is always normal and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
  Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}
  When $\lambda(i) = \mu$ for $i$ normal, write $\mu \xrightarrow{\text{normal}} \lambda$, and similar in the good case.

  The following statements, collectively known as \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev,Brundan} 
  They entirely characterize the socle of $\Res D^\lambda$, as well as semisimplicity od $\Res D^\lambda$.
  \begin{theorem}[Kleshchev-Brundan]
    We have the following isomorphisms of vector spaces
    \begin{align*}
      \Homarg{\SH'}{S^\mu,\Res D^\lambda} 
      &\simeq \begin{cases}
        k & \text{if }\mu \xrightarrow{\text{normal}} \lambda,\\
        0 & \text{otherwise}.
      \end{cases}\\
      \Homarg{\SH'}{D^\mu,\Res D^\lambda} 
      &\simeq \begin{cases}
        k & \text{if } \mu \xrightarrow{\text{good}} \lambda\\
        0 & \text{otherwise}
      \end{cases}
    \end{align*}
    and $\Res D^\lambda$ is semisimple if and only if every normal number in $\lambda$ is good.\qed
  \end{theorem}

  Using this, we immediately see that, for any rectangular partition $(m^\ell)$, we have
  \[
    \Res D^{(m^\ell)} \simeq D^{(m^{\ell-1},m-1)}.
  \]
  The non-rectangular two-row case is more complicated, but we may still describe it fully as follows.
  \begin{corollary}\label{D Restrictions}
    Suppose $r > 0$.
    Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
    \[
      \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
        D^{(n + r - 1,n)} & \text{if }e \mid r+2\\
        D^{(n + r,n-1)} &e \text{if }e\nmid r+2, \; e \mid r\\
        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & \text{if } e \nmid r+2,r
      \end{cases}
    \]
    Further, when $e \nmid r$ or $e \mid r + 2$, $\Res D^{(n+r,n)}$ is semisimple.
  \end{corollary}
  \begin{proof}
    This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
    \begin{align*}
      \beta_\lambda(1,2) &= r + 2\\
      \gamma_\lambda(1,2) &= r
    \end{align*}
    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ if and only if $e \nmid r + 2$.
    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ if and only if 1 is good;
    this is equivalent to $e \nmid r$.
  \end{proof}

  Now that we've characterized how $D^\lambda$ restrict, we can describe how strongly these restrictions characterize irreducibles.
  Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in the case that condition (i) of Corollary \ref{S irreducibility} holds and either $r \neq 0$ or $e \neq 4$.
  \begin{proposition}\label{Combinatorics}
    Let $\lambda$ be an $e$-regular partition of $2n + r$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r-2$.
        If $D^\lambda$ has the composition series 
        \begin{equation}\label{D Composition Series}
          0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
        \end{equation}
        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
        Then $\lambda = (n,n)$. 
    \end{enumerate}
  \end{proposition}
  \begin{proof}
    Note that $e > n$.
    Further, note that the above characterizations are necessary regardless of $e$-regularity;
    in the case that $\mu$ below fails too be $e$-regular, this proposition will prove that $\lambda$ does not satisfy \label{D Composition Series}, a contradiction.

    \textbf{(i)}
    Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)$, and let $\mu := (n + r,n)$.
    Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda \in \cbr{\varpi,\varsigma,\mu}$.
    We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series}, allowing us to conclude $\lambda = \mu$.

    If $\varpi$ or $\varsigma$ are not $e$-regular, then $D^\varpi = 0$ or $D^\varsigma = 0$, and we may immediately rule these out;
    henceforth assume that these are each $e$-regular.

    First suppose that that $\lambda = \varpi$.
    We will break into cases with $r$.
    \begin{itemize}
      \item Suppose that $r > 1$.
        Note that $e \nmid r + 1 = \beta_\varpi(1,2)$, so $2$ is normal.
        Further, $\gamma_\varpi(2,3) = n \not\equiv 0 \pmod e$, so 2 is good and $D^{(n+r-1,n-1,1)} \subset D^\varpi$, which is not a composition factor in \eqref{D Composition Series}.
        Hence, by the Jordan-H\"older theorem \cite{Etingof}, we have $\lambda \neq \varpi$.

      \item Suppose that $r = 1$.
        Then, $\varpi = (n,n,1)$ has $\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e$, giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$ as in the previous case.
    \end{itemize} 
  \iffalse % keeping just in case
   \begin{align*}
    \beta_{\varpi}(1,2)     &= r + 1 \\
    \beta_{\varpi}(1,3)     &= n + r + 1 \\
    \beta_{\varpi}(2,3)     &= n + 1\\
    \gamma_{\varpi}(1,2)    &= r\\
    \gamma_{\varpi}(1,3)    &= n + r\\
    \gamma_{\varpi}(2,3)    &= n\\
  \end{align*}
  \fi

  \vspace{5pt}
  Now suppose that $\lambda = \varsigma$ and break into cases with $r$:
  \begin{itemize}
    \item Suppose $r > 2$.
      Then, by Corollary \ref{D Restrictions}, we require that $e \nmid r$ and $e \mid r - 2$;
      these are not satisfied, so $\lambda \neq \varsigma$.
    \item Suppose $r = 2$.
      Then $\Res \, D^\varsigma \simeq D^{(n+1,n)}$ is irreducible, as $\varsigma = (n+1,n+1)$ has rows of the same length;
      this contradicts \eqref{D Composition Series}. 
    \item Suppose $r < 2$. 
      Then $\varsigma$ is not a partition.
  \end{itemize}
  This completes the proof.

  \textbf{(ii)}
  Since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
  This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
  if $\lambda = \varsigma$, then we have that $e \mid \beta_\varsigma(1,2) = 4$, a contradiction.
  Hence $\lambda = \mu$.
\end{proof}

@@

  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
  Then,
  \begin{align*}
    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
    &= 1 + \dots + q^{n + r}\\
    &= \brk{n + r + 1}_q.
  \end{align*}
  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
\end{proof}
\begin{theorem}\label{Irreducibility Theorem}
  Suppose that $e \nmid r+2,r+3,\dots,n+r+1$.
  Then, the representation $M_{2n + r}^r$ is irreducible. 
\end{theorem}
\begin{proof}
  We proceed by induction on $n$.
  Note that, by identification with the trivial and sign representation, the base case $n = 0$ is already proven.

@@

\bibliographystyle{numeric} 
 \bibliography{../RepBib}
\end{document}
